Resolving Limits Faced by Classical Machine Learning Approaches:\\Areas of Application for Collaborative Interactive Learning Techniques

### 2018-06-29 paper.tex
Add classification in Organic Computing

\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{xcolor}
\newcommand\notes[1]{\textcolor{red}{#1}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The area of \textit{Machine Learning (ML)} has experienced a high 
level of research interest in the last few years with it's underlying 
theory reaching back far into the 18Th century. Due to minimal 
costs for computation and the massive availability of data in the 
Internet recent research interest has been mainly focused on 
\textit{automatic ML (aML)}. In this ML paradigm a model 
(e.g.\ classifier, \dots) is being trained with a pre-labeled training 
set in order to make predictions on unknown unlabeled data. Problems arise 
in domains where data is rarely available or where the labeling process is 
too expensive (computationally or economically). Furthermore, real-world data 
can be uncertain, incomplete or contain noisy data. In these cases 
full automation is not reliable enough or even infeasible for specific 
domains. However, robust and trustworthy results are mandatory in a lot of 
applications like health informatics or autonomous vehicles. 
Therefore, systems are needed that interactively integrate knowledge from 
various experts, which can be collaborating humans or machines, in order 
to continuously improve results over a systems whole lifetime: So called 
\textit{Collaborative Interactive Learning (CIL)} systems.
This paper contributes in presenting an overview of classical ML approaches 
in comparison with CIL and outlines possible areas of application. 
\end{abstract}

@@

Hence, \textit{Collaborative Interactive Learning (CIL)} includes domain experts (humans) 
and other CIL systems in the decision/prediction making process as shown in 
Figure~\ref{fig:CIL}. The relatively new term describes a new 
generation of systems with
\begin{itemize}
    \item lifelong learning capabilities in order to continuously improve its 
        knowledge base
    \item and the ability to exchange knowledge with other CIL systems as well as humans 
        in order to improve the own knowledge and the one of other entities in a 
        bi-directional way\cite{CIL:sick}.
\end{itemize}
This article gives a brief introduction on possible areas of application for the CIL-approach. 
It starts with an overview of classical machine learning scenarios, discussing where they are 
facing limits and motivating the use of CIL\@. It then lists possble applications and concludes 
with a view on future research interests.\notes{Relation to Organic Computing?}

@@

\section{When is using CIL helpful?}
In etablierten ML Systemen muss für jede spezielle Anwendung ein eigenes Modell im Voraus 
entworfen und trainiert werden. ML Systeme haben also einen relativ schmalen Anwendungsrahmen. 
Die Idee bei CIL-Systemen ist, dass sie ein Leben lang lernen und selbstorganisiert Wissen 
aus verschiedenen Quellen sammeln und auswerten, um so gemeinsam mit anderen technischen 
und menschlichen Agenten kollaborierend und austauschend Probleme lösen\cite{CIL:sick}. 
Der CIL-Ansatz integriert also ganz bewusst andere intelligente Systeme 
(Menschen und Maschinen) in den Entscheidungsprozess, um für die einzelnen Entitäten 
ansonsten schwierige Probleme einfacher zu lösen.
Ein weiterer Unterschied zu klassischen Ansätzen stellt der wechselseitig Nutzen dar. 
Maschinen profitieren nicht nur von Trainingsdaten anderer Agenten, sondern leisten 
einen eigenen Beitrag, um Kollaborationsprozesse von Menschen aktiv zu unterstützen, indem 
sie ihre Wünsche und Bedürfnisse erkennen und entsprechend reagieren\cite{CIL:sick}.

\section{Classification of CIL in Organic Computing}
CIL-Systeme können sozusagen teilweise als organisch strukturierte Informationstechnologie verstanden 
werden, die sogenannte Selbst-x-Eigenschaften erfüllen\cite{Organic:schloer}\cite{Organic:schmeck}, 
sich also 
\begin{itemize}
    \item selbst konfigurieren, in dem Sinn, dass sie nicht von Entwicklern auf einen 
        Anwendungsfall ausgerichtet werden, 
    \item selbst optimieren, indem sie verschiedene Strategien des ML anwenden, um ihr 
        Wissen zu erweitern, 
    \item und sich selbst heilen und schützen, da Kooperation mit anderen System möglich ist.
\end{itemize}
Je nachdem welche Methoden des ML eingesetzt werden sind CIL-Systeme mehr oder weniger 
selbst erklärend\cite{Organic:schloer}.

\section{Application examples}

\begin{itemize}
    \item Clustering
        \begin{itemize}
            \item (clustering communities on Facebook for group target advertising (politics))
            \item Methods: k-Means, DJ-clustering? --> add paper ref
        \end{itemize}
    \item Stock trading
    \item Health domain
        \begin{itemize}
            \item Detecting cancer on radon, Prof. Sauer/Forwiss research?
            \item Growing number of users are using smartphones sensors and related devices for 
                collating a range of health information, track regularly and detect patterns (noise?, privacy?)
        \end{itemize}
    \item Industry 4.0
        \begin{itemize}
            \item quality assurance
        \end{itemize}
    \item Agriculture
        \begin{itemize}
            \item Detecting bad grains, $\rightarrow$ Hackzurich project
        \end{itemize}
\end{itemize}

@@

\begin{thebibliography}{1}
\bibitem{ML:mitchell}
    Mitchell, T. M. (1997). Machine learning. 1997. Burr Ridge, IL: McGraw Hill, 45(37), 870-877.
\bibitem{FoundationsOfML:mohri}
    Mohri, M., Rostamizadeh, A., \& Talwalkar, A. (2012). Foundations of machine learning. MIT press.
\bibitem{DisciplineOfML:mitchell}
    Mitchell, T. M. (2006). The discipline of machine learning (Vol. 9). Carnegie Mellon University, School of Computer Science, Machine Learning Department.
\bibitem{Prog2:bachmaier}
    Bachmaier, C. (2017). Lecture. Programming II\@. Faculty for Informatics and Mathematics, University of Passau, Germany.\notes{check this}
\bibitem{CIL:sick}
    Sick, B., Oeste-Rei{\ss}, S., Schmidt, A., Tomforde, S., \& Zweig, A. K. (2018). Collaborative Interactive Learning. Informatik-Spektrum, 41(1), 52-55.
\bibitem{Structure:corne}
    Corne, D., Dhaenens, C., \& Jourdan, L. (2012). Synergies between operations research and data mining: The emerging use of multi-objective approaches. European Journal of Operational Research, 221(3), 469-479.
\bibitem{ActiveToDedicated:calma}
    Calma, A., Leimeister, J. M., Lukowicz, P., Oeste-Rei{\ss}, S., Reitmaier, T., Schmidt, A., \dots \& Zweig, K. A. (2016, April). From active learning to dedicated collaborative interactive learning. In ARCS 2016; 29th International Conference on Architecture of Computing Systems; Proceedings of (pp. 1-8). VDE.
\bibitem{BrainInf:holzinger}
    Holzinger, A. (2016). Interactive machine learning for health informatics: when do we need the human-in-the-loop?. Brain Informatics, 3(2), 119-131.
\bibitem{MLStudiesUsingCheckers:samuel}
    Samuel, A. L. (1959). Some studies in machine learning using the game of checkers. IBM Journal of research and development, 3(3), 210-229.
\bibitem{Organic:schloer}
    M{\"u}ller-Schloer, C., von der Malsburg, C., \& W{\"u}rt, R. P. (2004). Organic computing. Informatik-Spektrum, 27(4), 332-336.
\bibitem{Organic:schmeck}
    Schmeck, H. (2005, May). Organic computing-a new vision for distributed embedded systems. In Object-Oriented Real-Time Distributed Computing, 2005. ISORC 2005. Eighth IEEE International Symposium on (pp. 201-203). IEEE.
\end{thebibliography}

>>>>

\usepackage{xcolor}
\newcommand\notes[1]{\textcolor{red}{#1}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The area of \textit{Machine Learning (ML)} has experienced a high 
level of research interest in the last few years with it's underlying 
theory reaching back far into the 18Th century. Due to minimal 
costs for computation and the massive availability of data in the 
Internet recent research interest has been mainly focused on 
\textit{automatic ML (aML)}. In this ML paradigm a model 
(e.g.\ classifier, \dots) is being trained with a pre-labeled training 
set in order to make predictions on unknown unlabeled data. Problems arise 
in domains where data is rarely available or where the labeling process is 
too expensive (computationally or economically). Furthermore, real-world data 
can be uncertain, incomplete or contain noisy data. In these cases 
full automation is not reliable enough or even infeasible for specific 
domains. However, robust and trustworthy results are mandatory in a lot of 
applications like health informatics or autonomous vehicles. 
Therefore, systems are needed that interactively integrate knowledge from 
various experts, which can be collaborating humans or machines, in order 
to continuously improve results over a systems whole lifetime: So called 
\textit{Collaborative Interactive Learning (CIL)} systems.
This paper contributes in presenting an overview of classical ML approaches 
in comparison with CIL and outlines possible areas of application. 
\notes{Abstract kuerzen, 18th Jahrhundert interessiert niemanden.}
\end{abstract}

@@

Hence, \textit{Collaborative Interactive Learning (CIL)} includes domain experts (humans) 
and other CIL systems in the decision/prediction making process as shown in 
Figure~\ref{fig:CIL}. The relatively new term describes a new 
generation of systems with
\begin{itemize}
    \item lifelong learning capabilities in order to continuously improve its 
        knowledge base
    \item and the ability to exchange knowledge with other CIL systems as well as humans 
        in order to improve the own knowledge and the one of other entities in a 
        bi-directional way\cite{CIL:sick}.
\end{itemize}

This article gives a brief introduction on possible areas of application for the CIL-approach. 
It starts with an overview of classical machine learning scenarios, discussing where they are 
facing limits and motivating the use of CIL\@. It then lists possble applications and concludes 
with a view on future research interests.\notes{Relation to Organic Computing?}

@@

\section{When is using CIL helpful?}\label{AdvantageOfCIL}
In etablierten ML Systemen muss für jede spezielle Anwendung ein eigenes Modell im Voraus 
entworfen und trainiert werden. ML Systeme haben also einen relativ schmalen Anwendungsrahmen. 
Die Idee bei CIL-Systemen ist, dass sie ein Leben lang lernen und selbstorganisiert Wissen 
aus verschiedenen Quellen sammeln und auswerten, um so gemeinsam mit anderen technischen 
und menschlichen Agenten kollaborierend und austauschend Probleme lösen\cite{CIL:sick}. 
Der CIL-Ansatz integriert also ganz bewusst andere intelligente Systeme 
(Menschen und Maschinen) in den Entscheidungsprozess, um für die einzelnen Entitäten 
ansonsten schwierige Probleme einfacher zu lösen.
Ein weiterer Unterschied zu klassischen Ansätzen stellt der wechselseitig Nutzen dar. 
Maschinen profitieren nicht nur von Trainingsdaten anderer Agenten, sondern leisten 
einen eigenen Beitrag, um Kollaborationsprozesse von Menschen aktiv zu unterstützen, indem 
sie ihre Wünsche und Bedürfnisse erkennen und entsprechend reagieren\cite{CIL:sick}.
\notes{D-CIL und O-CIL, obwohl man unterscheidet, betrachten wir hier nur allgemeines Modell.}

\section{Classification of CIL in Organic Computing}
CIL-Systeme können sozusagen teilweise als organisch strukturierte Informationstechnologie verstanden 
werden, die sogenannte Selbst-x-Eigenschaften erfüllen\cite{Organic:schloer}\cite{Organic:schmeck}, 
sich also 
\begin{itemize}
    \item selbst konfigurieren, in dem Sinn, dass sie nicht von Entwicklern auf einen 
        Anwendungsfall ausgerichtet werden, 
    \item selbst optimieren, indem sie verschiedene Strategien des ML anwenden, um ihr 
        Wissen zu erweitern, 
    \item und sich selbst heilen und schützen, da Kooperation mit anderen System möglich ist.
\end{itemize}
Je nachdem welche Methoden des ML eingesetzt werden, sind CIL-Systeme in der Entwicklung auch 
mehr oder weniger selbst erklärend\cite{Organic:schloer}.

\section{Application examples}
\subsection{Clustering}

\subsection{Health Domain}

\subsection{Industry and Manufacturing}

\subsection{Agriculture}

\begin{itemize}
    \item Clustering
        \begin{itemize}
            \item (clustering communities on Facebook for group target advertising (politics))
            \item Methods: k-Means, DJ-clustering? --> add paper ref
        \end{itemize}
    \item Health
        \begin{itemize}
            \item Detecting cancer on radon, Prof. Sauer/Forwiss research?
            \item Growing number of users are using smartphones sensors and related devices for 
                collating a range of health information, track regularly and detect patterns (noise?, privacy?)
        \end{itemize}
    \item Industry and Manufacturing
        \begin{itemize}
            \item quality assurance
        \end{itemize}
    \item Agriculture
        \begin{itemize}
            \item Detecting bad grains, $\rightarrow$ Hackzurich project
        \end{itemize}
\end{itemize}

@@

\begin{thebibliography}{1}
\bibitem{ML:mitchell}
    Mitchell, T. M. (1997). Machine learning. 1997. Burr Ridge, IL: McGraw Hill, 45(37), 870-877.
\bibitem{FoundationsOfML:mohri}
    Mohri, M., Rostamizadeh, A., \& Talwalkar, A. (2012). Foundations of machine learning. MIT press.
\bibitem{DisciplineOfML:mitchell}
    Mitchell, T. M. (2006). The discipline of machine learning (Vol. 9). Carnegie Mellon University, School of Computer Science, Machine Learning Department.
\bibitem{Prog2:bachmaier}
    Bachmaier, C. (2017). Lecture. Programming II\@. Faculty for Informatics and Mathematics, University of Passau, Germany.\notes{check this}
\bibitem{CIL:sick}
    Sick, B., Oeste-Rei{\ss}, S., Schmidt, A., Tomforde, S., \& Zweig, A. K. (2018). Collaborative Interactive Learning. Informatik-Spektrum, 41(1), 52-55.
\bibitem{Structure:corne}
    Corne, D., Dhaenens, C., \& Jourdan, L. (2012). Synergies between operations research and data mining: The emerging use of multi-objective approaches. European Journal of Operational Research, 221(3), 469-479.
\bibitem{ActiveToDedicated:calma}
    Calma, A., Leimeister, J. M., Lukowicz, P., Oeste-Rei{\ss}, S., Reitmaier, T., Schmidt, A., \dots \& Zweig, K. A. (2016, April). From active learning to dedicated collaborative interactive learning. In ARCS 2016; 29th International Conference on Architecture of Computing Systems; Proceedings of (pp. 1-8). VDE.
\bibitem{BrainInf:holzinger}
    Holzinger, A. (2016). Interactive machine learning for health informatics: when do we need the human-in-the-loop?. Brain Informatics, 3(2), 119-131.
\bibitem{MLStudiesUsingCheckers:samuel}
    Samuel, A. L. (1959). Some studies in machine learning using the game of checkers. IBM Journal of research and development, 3(3), 210-229.
\bibitem{Organic:schloer}
    M{\"u}ller-Schloer, C., von der Malsburg, C., \& W{\"u}rt, R. P. (2004). Organic computing. Informatik-Spektrum, 27(4), 332-336.
\bibitem{Organic:schmeck}
    Schmeck, H. (2005, May). Organic computing-a new vision for distributed embedded systems. In Object-Oriented Real-Time Distributed Computing, 2005. ISORC 2005. Eighth IEEE International Symposium on (pp. 201-203). IEEE.
\bibitem{Foldit:web}
    The Science Behind Foldit. (n.d.). Retrieved June 29, 2018, from https://fold.it/portal/info/about. University of Washington, Departments of Computer Science \& Engineering and Biochemistry.
\end{thebibliography}
